%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant with Data Science | ScrumMaster} % Job title
    {IBM Japan, Ltd.} % Organization
    {Tokyo, Japan} % Location
    {Apr. 2016 - Today} % Date(s)
    {
      \begin{cvenumerate} % Description(s) of tasks/responsibilities
        \item {[Pharmaceutical and Insurance, 2020] Leveraging the experiences of Agile, Lean Startup, and Statistics to plan a system to keep treatments for patients who suffer from osteoporosis with clients of both Pharmaceutical and Insurance.}
        \item {[Automotive, 2019] Lead and ScrumMaster of 5 client members of Analytics team. Explored magic-numbers; KPIs and Visualized some metrics to support Product Owner's dicision-making. Through this project, client's in-house data scientists team acquired Agile and Data-Informed culture.}
        \item {[Pharmaceutical, 2019] Lead and ScrumMaster of 7 members of Analytics team. Developed a web-app to support medical representatives recommending sales activities; to whom, what, and how.}
        \item {[Automotive, 2019] Lead and ScrumMaster of 2 members of Analytics team. Visualized commands of a system about crash simulations to optimize the operation.}
        \item {[Automotive, 2018] Lead and ScrumMaster of 3 members of Analytics team. Developed a system of demand-forecasting for spare parts of motor cycles.}
        \item {[Pharmacy, 2018] Developed a function to match drugs and diseases by fuzzy matching to support pharmacists. Collaborated with other developers to develop web-app including the function.　\href{https://www.ibm.com/think/jp-ja/business/sakura-ai/}{\textcolor{blue}{...Click Here}}}
        \item {[Automotive, 2018] Analyzed the market for a robot product to develop a new one. Supported to explore the early adopters' features by questionnaires and depth interviews.}
        \item {[Pharmaceutical, 2017] Developed a function to optimize sales activities of medical representatives. Collaborated with other developers to develop web-app including the optimizer.}
        \item {[Pharmaceutical, 2017] Planned and Tested a function by using the text data of medical records, to notify doctors that patients who suffer from mental diseases with a difficulty to keep receiving treatments.}
        \item {[Pharmaceutical, 2016] Cleaned and Organized the text data of medical records about mental diseases to predict the probability of becoming a long-term hospitalized patient (>90 or >180 days). \href{https://www.ibm.com/downloads/cas/VVYMQYLZ}{\textcolor{blue}{...Click Here}}}
        \item {[Banking, 2016] Cleaned and Organized the text data of reports about money laundering, to predict the probability of an illegal activities.}
      \end{cvenumerate}
    }
%---------------------------------------------------------
\end{cventries}
